State of the Practice for Lattice Boltzmann Method Software

### 2022-04-21 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revision complete, now requires proof reading

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with Harvard style bibliographic references

@@

\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}
\usepackage{paralist}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{pbox}

@@

The top LBM projects have adopted techniques for software verification that get
around the oracle problem (mentioned earlier in Section~\ppref{P_Correctness}). In
the absence of a general test oracle, the following techniques have been adopted
by LBM developers:

@@

\subsection{Grow the Number of Contributors} \label{Sec_GrowContributors}

@@

\begin{itemize}
	\item Add roadmap documentation showing what is planned for the future.
	\wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Add a code of conduct to explicitly show how developers should treat
	one another. \wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Increase the use and enforcement of programming style guides.
	\wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Use checklists to ensure best practices are followed by developers.
	\wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Include uninstall instructions. \wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Increase the amount of API documentation. \wss{reason} (Section~\ref{Sec_CompareArtifacts})
	\item Increase the use of CI. \wss{reason} (Section~\ref{Sec_CompareTools})
	\item Explicitly document the software's motivation and design principles.
	\wss{reason - where is this discussed the first time - should add more
	information there.} (Section~\ref{Sec_CompareMethodologies})
\end{itemize}

For insight into devising future methods and tools, we interviewed four
developers to learn about their pain points (Section~\ref{painpoints}).  The
identified pain points \wss{expand into bullet list} include lack of development
time, lack of software development experience, lack of incentive and funding,
lack of external support, technology hurdles, ensuring correctness, usability,
technical debt and documentation quality.  We found
(Section~\ref{Sec_AddressConcerns} that developers are currently creating
practices to address these pain points, including \wss{expand into list}:
designing for change \wss{what pain point? why? do the same for the others in
the list}, circumventing the oracle testing problem, and prioritizing
documentation and usability.  To plan for future best practices, we identified
eight potential directions (Section~\ref{Sec_Recommendations}), in order of
increasing development effort:

\begin{enumerate}
	\item Employ linters. \wss{reason}  (Section~\ref{Sec_Linters})
	\item Conduct rigorous peer reviews. \wss{reason}
	(Section~\ref{Sec_PeerReview})
	\item Write and submit papers on software. \wss{reason}
	(Section~\ref{Sec_MorePapers})
	\item Apply advice from the open-source community on how to grow the number
	of contributors. \wss{reason - change this to documentation?}
	(Section~\ref{Sec_GrowContributors})
	\item Further address the oracle problem for testing.  \wss{reason}
	(Section~\ref{Sec_FurtherOracle})
	\item Augment theory manuals to include requirements information.
	\wss{reason} (Section~\ref{Sec_AugTheoryMans})
	\item Improve re-runnability, repeatability, reproducibility and
	replicability. \wss{reason}  (Section~\ref{Sec_Reproducibility})
	\item Generate all things. \wss{reason}  (Section~\ref{Sec_GenAllThings})
\end{enumerate}

>>>>

%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with Harvard style bibliographic references

@@

\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}
\usepackage{paralist}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{pbox}

@@

The top LBM projects have adopted techniques for software verification that get
around the oracle problem (mentioned earlier in \ppref{P_Correctness}). In the
absence of a general test oracle, the following techniques have been adopted by
LBM developers:

@@

\subsection{Follow Advice From the Open-Source Community to Grow the Number of Contributors} \label{Sec_GrowContributors}

@@

\begin{itemize}
	\item Add roadmap documentation showing what is planned for the future to
	provide continuity of purpose, facilitate stakeholder collaboration and
	assist with prioritization. (Section~\ref{Sec_CompareArtifacts})
	\item Add a code of conduct to improve inclusivity and attract a wider pool
	of collaborators. (Section~\ref{Sec_CompareArtifacts})
	\item Increase the use and enforcement of programming style guides to improve understandability and productivity. (Section~\ref{Sec_CompareArtifacts})
	\item Use checklists to ensure best practices are followed by developers. (Section~\ref{Sec_CompareArtifacts})
	\item Include uninstall instructions as a courtesy to users that wish to
	save space and avoid polluting their build system.
	(Section~\ref{Sec_CompareArtifacts})
	\item Increase the amount of API documentation to improve API
	understandability. (Section~\ref{Sec_CompareArtifacts})
	\item Increase the use of CI to remove headaches associated with a separate
	integration phase, quickly detect and remove bugs and improve productivity,
	since developers will always working from a stable base.
	(Section~\ref{Sec_CompareTools})
	\item Explicitly document the software's motivation and design principles to
	assist with on-boarding new developers.
	(Section~\ref{Sec_CompareMethodologies})
\end{itemize}

For insight into devising future methods and tools, we interviewed four
developers to learn about their pain points (Section~\ref{painpoints}).  The
identified pain points include:

\begin{description}
\item [\ppref{P_LackDevTime}] Lack of development time, %1
\item [\ppref{P_LackSoftDevExp}] Lack of software development experience, %2
\item [\ppref{P_LackFunding}] Lack of incentive and funding, %3
\item [\ppref{P_LackExtSupport}] Lack of external support, %4
\item [\ppref{P_TechnologyHurdles}] Technology hurdles, %5
\item [\ppref{P_Correctness}] Ensuring correctness, %6
\item [\ppref{P_Usability}] Usability, %7
\item [\ppref{P_TechDebt}] Technical debt, and %8
\item [\ppref{P_Documentation}] Documentation quality. %9
\end{description}

We found (Section~\ref{Sec_AddressConcerns}) that developers are currently
creating practices to address these pain points.  To address technical debt
(\ppref{P_TechDebt}) some developers have committed to designing for change
(Section~\ref{Sec_DesForChange}). To improve correctness (\ppref{P_Correctness})
developers are finding ways to circumvent the oracle testing problem, such as
using peer review and pseudo-oracles (Section~\ref{SecReproducibility}).
Developers have prioritized documentation and usability
(Section~\ref{Sec_RecommendDoc} to address the pain points of documentation and
usability challenges (\ppref{P_Usability} and \ppref{P_Documentation}).  For the
pain point related to external support (\ppref{P_LackExtSupport}), we found that
this is currently addressed by groups like \href{https://bssw.io/} {Better
Scientific Software (BSSw)},
\href{https://www.software.ac.uk/} {Software Sustainability Institute}
\citep{CrouchEtAl2013}, and \href{https://software-carpentry.org/}{Software
Carpentry} \citep{WilsonAndLumsdaine2006, Wilson2016}. Other pain points do not
seem to be addressed by current practices.  This motivates our eight
recommendations for potential future directions
(Section~\ref{Sec_Recommendations}), in order of increasing development effort:

\begin{enumerate}
	\item Employ linters to address \ppref{P_LackDevTime}, \ppref{P_LackSoftDevExp}, \ppref{P_TechnologyHurdles} and \ppref{P_TechDebt}. (Section~\ref{Sec_Linters})
	\item Conduct rigorous peer reviews to address \ppref{P_LackDevTime},
	\ppref{P_LackSoftDevExp}, \ppref{P_TechnologyHurdles} and
	\ppref{P_TechDebt}.	(Section~\ref{Sec_PeerReview})
	\item Write and submit papers on software to address \ppref{P_LackFunding}.
	(Section~\ref{Sec_MorePapers})
	\item Apply advice from the open-source community on how to grow the number
	of contributors to address \ppref{P_LackDevTime}.
	(Section~\ref{Sec_GrowContributors})
	\item Further address the oracle problem for testing, with techniques such as the method of manufactured solutions and metamorphic testing, to address
	\ppref{P_Correctness}. (Section~\ref{Sec_FurtherOracle})
	\item Augment theory manuals to include requirements information to address
	\ppref{P_LackDevTime}, \ppref{P_Usability} and \ppref{P_Documentation}.
	(Section~\ref{Sec_AugTheoryMans})
	\item Improve re-runnability, repeatability, reproducibility and
	replicability to improve \ppref{P_Correctness}.
	(Section~\ref{Sec_Reproducibility})
	\item Use Domain Specific Modelling to generate all LBM code, build scripts,
	documentation, test cases from a stable knowledge base to address
	\ppref{P_LackDevTime}, \ppref{P_LackSoftDevExp},
	\ppref{P_TechnologyHurdles}, \ppref{P_Correctness}, \ppref{P_Usability},
	\ppref{P_TechDebt} and \ppref{P_Documentation}.
	(Section~\ref{Sec_GenAllThings})
\end{enumerate}
